An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2012-04-03 Paper.tex
Adjusted LaTeX to designate 'intermetiate' versions.
I've added a footnote to the version date that, when present, explains that
the current version of the paper is no less than the date listed, but
may be higher.

\documentclass[12pt,fleqn]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,eco}
\usepackage[T1]{fontenc}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/simulationdefinitions}
\input{tex/empiricalresults}

@@

\title{An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models} \date{\today}
\maketitle

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
    \sum_{t=2}^T \E x_{t-1} y_t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that includes
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
    long run variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
    x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} |\bar{f}_{i}| > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{i \notin
      M_{j-1}} \tfrac{1}{\hat{\sigma}_i^{*}}|\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1})|$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$
    and $\bar f_i > 0$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of rejecting
    one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \mds\ with respect to $\mathcal{F}_{lt}$
    against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
    $p \to 0$ and $P p \to \infty$ as $T \to \infty$ (for the
    stationary bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$
    (for the moving or circular block bootstraps) then the procedure
    outlined above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of null
    hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\beta_{0}) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_{0}) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\beta_{0}) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0})
    = 0$ for all $s$.
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector.
    Then $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
    circular blocks, or stationary bootstrap with block lengths drawn
    from the geometric distribution, and $b$ satisfies $b \to \infty$
    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
    circular blocks bootstraps and is the expected block length of the
    stationary bootstrap.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that the
modified version of \citepos{ClW:07} statistic performs similarly to
their original test in the situations they study.\footnote{All of
  these simulations were programmed in R \citep{R:2-13-0} and use the
  \textsc{MASS} \citep{VeR:02}, xtable \citep{Dah:09}, and dbframe
  \citep{Cal:10b} packages.  Version
  information is listed in the bibliography.}  I'll use both of the
\dgp s they consider as well as a modification to study the
performance of the statistics if there is instability.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a 10-year window.  The
predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses 10
observations.\footnote{This statistical analysis was conducted in R
  \citep{R:2-13-0} using the xtable \citep{Dah:09}, Hmisc
  \citep{Har:10}, and dbframe \citep{Cal:10b} packages; version
  information for each package is listed in the bibliography.}

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-10\% critical value (1.28) and the
critical value estimated by the procedure of Theorem~\ref{res:2}
(\empiricalcriticalvalue).\footnote{The bootstrap uses 999
  replications with i.i.d. sampling, as proposed in Part~(\ref{it:1})
  of Theorem~\ref{res:2}.}  Three predictors are significant at the
naive critical values for both the original and bounded forecasts: the
dividend yield, long term interest rate, and book to market ratio.
But none are significant after accounting for data snooping, which
highlights the importance of these methods.  The median forecast is
significant using conventional critical values as well, but not the
corrected values.

>>>>

\documentclass[10pt,fleqn,draft]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round]{natbib}
\usepackage[top=1in,left=1.75in,right=1.75in,bottom=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/simulationdefinitions}
\input{tex/empiricsdefinitions}
\input{tex/empiricalresults}

% redfine heading styles
\makeatletter
\renewcommand\section{\@startsection%
{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
{\normalfont\normalsize\bfseries\large\raggedright}}
\makeatother

@@

\title{An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models}

\date{\input{VERSION% <- allows VERSION to have comments
}}
\maketitle

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
    \sum_{t=2}^T \E x_{t-1} y_t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that includes
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
    long run variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
    x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} |\bar{f}_{i}| > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{i \notin
      M_{j-1}} \tfrac{1}{\hat{\sigma}_i^{*}}|\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1})|$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$
    and $\bar f_i > 0$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \textsl{\mds} with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of rejecting
    one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \textsl{\mds} with respect to $\mathcal{F}_{lt}$
    against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
    $p \to 0$ and $P p \to \infty$ as $T \to \infty$ (for the
    stationary bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$
    (for the moving or circular block bootstraps) then the procedure
    outlined above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of null
    hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\beta_{0}) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_{0}) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\beta_{0}) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0})
    = 0$ for all $s$.
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector.
    Then $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
    circular blocks, or stationary bootstrap with block lengths drawn
    from the geometric distribution, and $b$ satisfies $b \to \infty$
    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
    circular blocks bootstraps and is the expected block length of the
    stationary bootstrap.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that the
modified version of \citepos{ClW:07} statistic performs similarly to
their original test in the situations they study.\footnote{All of
  these simulations were programmed in R \citep[version 2.14.0]{R} and
  use the \textsc{MASS} \citep[version info]{VeR:02}, xtable
  \citep[version info]{Dah:09}, and dbframe \citep[version
  0.2.1]{Cal:10b} packages.  For details on the programming, please
  see the supplemental appendices \citep{Cal:11f,Cal:11g,Cal:11h}.}
I'll use both of the \dgp s they consider as well as a modification to
study the performance of the statistics if there is instability.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.\footnote{This statistical analysis was
  conducted in R \citep{R} using the xtable \citep[version]{Dah:09},
  Hmisc \citep[version]{Har:10}, and dbframe \citep[version
  0.2.1]{Cal:10b} packages; please see the supplemental appendices for
  details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-\bootsize\% critical value (1.28)
and the critical value estimated by the procedure of
Theorem~\ref{res:2} (\empiricalcriticalvalue).\footnote{The bootstrap
  uses \nboot\ replications with i.i.d. sampling, as proposed in
  Part~(\ref{it:1}) of Theorem~\ref{res:2}.}  Three predictors are
significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio.  But none are significant after accounting for
data snooping, which highlights the importance of these methods.  The
median forecast is significant using conventional critical values as
well, but not the corrected values.
